Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-23 manuscript/main.tex
updated diffusion results with one tailed test
added wordcount to doc
revising intro

\singlespacing
\begin{abstract} 
    \noindent The identification of substantively similar policy proposals in both proposed and adopted legislation is important to scholars of public policy diffusion and legislative politics. Conventional, manual, approaches are prohibitively costly in constructing datasets that accurately represent policymaking across policy domains, geographic units, and/or time. We propose the use of text-sequencing algorithms, applied to legislative text, to identify bills that introduce similar policy proposals. We present three ground truth tests, applied to a corpus of 500,000 bills from US-state legislatures. First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse. Second, we show that bills classified by the National Council of State Legislatures as covering the same policies exhibit a high degree of text re-use. Third, we show that rates of text reuse across state borders correlate strongly with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).

@@

Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract segments of text in pieces of legislation that communicate similar policy enactments. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purposes of policy diffusion research. Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similarity rather than a dichotomy of equivalence.

@@

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
 & Coefficient & p-value & Coefficient & p-value \\ 
  \hline
Intercept & -33577305.97 & 0.00 & 10.04 & 0.00 \\ 
  Diffusion Tie & 2423709.31 & 0.05 & 0.27 & 0.10 \\ 
  Coverage & 10938819.90 & 0.00 & 1.38 & 0.00 \\ 
  \hline
\end{tabular}
\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

>>>>

%Words in text: 6036
%Words in headers: 60
%Words outside text (captions, etc.): 502
%Number of headers: 17
%Number of floats/tables/figures: 8
%Number of math inlines: 67
%Number of math displayed: 3

\singlespacing
\begin{abstract} 
    \noindent The identification of substantively similar policy proposals in both proposed and adopted legislation is important to scholars of public policy diffusion and legislative politics. Conventional, manual, approaches are prohibitively costly in constructing datasets that accurately represent policymaking across policy domains, jurisdictions, or time. We propose the use of text-sequencing algorithms, applied to legislative text, to identify bills that introduce similar policy proposals. We present three ground truth tests, applied to a corpus of 500,000 bills from US-state legislatures. First, we show that bills introduced by ideologically similar sponsors are more likely to exhibit a high degree of text reuse. Second, we show that bills classified by the National Council of State Legislatures as covering the same policies exhibit a high degree of text re-use. Third, we show that rates of text reuse across state borders correlate with the diffusion networks recently introduced by Desmarais, Harden and Boehmke (2015).

@@

Through the development of an automated text analytic approach to measuring policy similarity, we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract segments of text in pieces of legislation that communicate similar policy enactments. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purposes of public policy policy research. Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similarity rather than a dichotomy of equivalence.

@@

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
 & Coefficient & p-value & Coefficient & p-value \\ 
\end{tabular}
\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}
